### 2019-10-21 ch8_discussion/content.tex
~

We proposed a novel algorithm for inferring case-wise gene regulatory interactions. While we demonstrated the methodology by inferring 22'122 cell-specific GRNs and 14'963 sample-specific GRNs from the Tabula Muris and TCGA projects respectively, further interpretation of these results needs to be perform to further validate the usefulness of the method.

>>>>

We proposed a novel algorithm for inferring case-wise gene regulatory interactions (Chapter~\ref{chap:bred}). While we demonstrated the methodology by inferring 14'963 sample-specific GRNs from the TCGA project, further interpretation of these results needs to be perform to validate the usefulness of the method.

### 2019-10-21 chX_backmatter.tex
update
~

\section{Professional Experience}
\textit{Ph.D. student in Bioinformatics} \\
\hspace*{2 ex} Ghent University, Belgium, September 2013 -- now \\
\textit{Laboratory assistant (summer job)} \\
\hspace*{2 ex} Bloedtransfusiecentrum Gent, Belgium, July (2009 -- 2012)

@@

\begin{table}[ht!]
	\caption{\textbf{Contibutions to open-source software.} Following abbreviations denote the relation with respect to the package: \textit{aut} Author, \textit{ctb} Contributor. Yearly download statistics are based on the number of downloads between 2019-08-01 and 2019-10-14. CRAN download statistics are retrieved from the Rstudio CRAN mirror only; other CRAN mirrors do not track download statistics. In addition, many of the dynverse packages have only recently been published on CRAN. For Github repositories, no download statistics could be retrieved. } \label{tab:packages}

	\centering\fontsize{9}{11}\selectfont
	\begin{tabularx}{\linewidth}{|p{2cm}llp{1.5cm}X|}
		\hline
		Name & Role & Host & Downloads per year & Description \\ \hline\hline
		\cranpkg{babelwhale} & aut & CRAN & 5810 & Interacting with Docker and Singularity containers \\
		\cranpkg{diffusionMap} & aut & CRAN & 30'450 & Implements diffusion map method of data parameterization \\
		\githubpkg{dynverse}{dynbenchmark} & aut & Github & \notavailable & Pipeline for benchmarking trajectory inference methods \\
		\cranpkg{dyndimred} & aut & CRAN & 5535 & Applying dimensionality reduction methods \\
		\githubpkg{dynverse}{dyneval} & aut & Github & \notavailable & Evaluating trajectory inference methods \\
		\githubpkg{dynverse}{dynfeature} & aut & Github & \notavailable & Calculating feature importance scores from trajectories \\
		\githubpkg{dynverse}{dyngen} & aut & Github & \notavailable & Simulating single-cell data using gene regulatory networks \\
		\githubpkg{dynverse}{dynguidelines} & aut & Github & \notavailable & User guidelines for trajectory inference \\
		\githubpkg{dynverse}{dynmethods} & aut & Github & \notavailable & A collection of wrappers for trajectory inference methods \\
		\githubpkg{dynverse}{dyno} & aut & Github & \notavailable & A pipeline for inferring, visualising and interpreting trajectories \\
		\cranpkg{dynparam} & aut & CRAN & 3265 & Creating meta-information for parameters \\
		\githubpkg{dynverse}{dynplot} & aut & Github & \notavailable & A simple visualisation library for trajectories \\
		\githubpkg{dynverse}{dynplot2} & aut & Github & \notavailable & A fully customisable visualisation library for trajectories \\
		\githubpkg{dynverse}{dyntoy} & aut & Github & \notavailable & Generating simple toy data of cellular differentiation \\
		\cranpkg{dynutils} & aut & CRAN & 13'130 & Common functionality for the dynverse packages \\
		\cranpkg{dynwrap} & aut & CRAN & 990 & A common format for trajectories \\
		\cranpkg{GillespieSSA} & aut & CRAN & 7880 & Gillespie's Stochastic Simulation Algorithm (SSA) \\
		\cranpkg{GillespieSSA2} & aut & CRAN & 4950 & Gillespie's Stochastic Simulation Algorithm for Impatient People \\
		\githubpkg{dynverse}{gng} & aut & Github & \notavailable & Growing Neural Gas implemented in Rcpp \\
		\cranpkg{incgraph} & aut & CRAN & 3565 & Incremental graphlet counting for network optimisation \\
		\cranpkg{lmds} & aut & CRAN & 815 & Landmark Multi-Dimensional Scaling \\
		\cranpkg{princurve} & aut & CRAN & 29'100 & Fits a principal curve in arbitrary dimension \\
		\cranpkg{proxyC} & aut & CRAN & 117'480 & Computes proximity in large sparse matrices \\
		\cranpkg{qsub} & aut & CRAN & 3585 & Running commands remotely on gridengine clusters \\
		\cranpkg{SCORPIUS} & aut & CRAN & 4520 & Inferring developmental chronologies from single-cell RNA sequencing data \\ \hline\hline

@@

\section{Sources of funding}
This study was supported by the Fonds Wetenschappelijk Onderzoek (11Y6218N).

>>>>

\section{Professional Experience}
\textit{Ph.D. student in Computer Science} \\
\hspace*{2 ex} Ghent University, Belgium, September 2013 -- now \\
\textit{Laboratory assistant (summer job)} \\
\hspace*{2 ex} Bloedtransfusiecentrum Gent, Belgium, July (2009 -- 2012)

@@

\begin{table}[ht!]
	\caption{\textbf{Contibutions to open-source software.} Following abbreviations denote the relation with respect to the package: \textit{aut} Author, \textit{ctb} Contributor. Yearly download statistics are based on the number of downloads between 2019-10-01 and 2019-10-21. CRAN download statistics are retrieved from the Rstudio CRAN mirror only; other CRAN mirrors do not track download statistics. In addition, many of the dynverse packages have only recently been published on CRAN. For Github repositories, no download statistics could be retrieved. } \label{tab:packages}

	\centering\fontsize{9}{11}\selectfont
	\begin{tabularx}{\linewidth}{|p{2cm}llp{1.5cm}X|}
		\hline
		Name & Role & Host & Downloads per year & Description \\ \hline\hline
		\cranpkg{babelwhale} & aut & CRAN & 9800 & Interacting with Docker and Singularity containers \\
		\cranpkg{diffusionMap} & aut & CRAN & 27'850 & Implements diffusion map method of data parameterization \\
		\githubpkg{dynverse}{dynbenchmark} & aut & Github & \notavailable & Pipeline for benchmarking trajectory inference methods \\
		\cranpkg{dyndimred} & aut & CRAN & 4708 & Applying dimensionality reduction methods \\
		\githubpkg{dynverse}{dyneval} & aut & Github & \notavailable & Evaluating trajectory inference methods \\
		\githubpkg{dynverse}{dynfeature} & aut & Github & \notavailable & Calculating feature importance scores from trajectories \\
		\githubpkg{dynverse}{dyngen} & aut & Github & \notavailable & Simulating single-cell data using gene regulatory networks \\
		\githubpkg{dynverse}{dynguidelines} & aut & Github & \notavailable & User guidelines for trajectory inference \\
		\githubpkg{dynverse}{dynmethods} & aut & Github & \notavailable & A collection of wrappers for trajectory inference methods \\
		\githubpkg{dynverse}{dyno} & aut & Github & \notavailable & A pipeline for inferring, visualising and interpreting trajectories \\
		\cranpkg{dynparam} & aut & CRAN & 2810 & Creating meta-information for parameters \\
		\githubpkg{dynverse}{dynplot} & aut & Github & \notavailable & A simple visualisation library for trajectories \\
		\githubpkg{dynverse}{dynplot2} & aut & Github & \notavailable & A fully customisable visualisation library for trajectories \\
		\githubpkg{dynverse}{dyntoy} & aut & Github & \notavailable & Generating simple toy data of cellular differentiation \\
		\cranpkg{dynutils} & aut & CRAN & 32'668 & Common functionality for the dynverse packages \\
		\cranpkg{dynwrap} & aut & CRAN & 4636 & A common format for trajectories \\
		\cranpkg{GillespieSSA} & aut & CRAN & 7118 & Gillespie's Stochastic Simulation Algorithm (SSA) \\
		\cranpkg{GillespieSSA2} & aut & CRAN & 4950 & Gillespie's Stochastic Simulation Algorithm for Impatient People \\
		\githubpkg{dynverse}{gng} & aut & Github & \notavailable & Growing Neural Gas implemented in Rcpp \\
		\cranpkg{incgraph} & aut & CRAN & 3565 & Incremental graphlet counting for network optimisation \\
		\cranpkg{lmds} & aut & CRAN & 23'' & Landmark Multi-Dimensional Scaling \\
		\cranpkg{princurve} & aut & CRAN & 29'100 & Fits a principal curve in arbitrary dimension \\
		\cranpkg{proxyC} & aut & CRAN & 117'480 & Computes proximity in large sparse matrices \\
		\cranpkg{qsub} & aut & CRAN & 3585 & Running commands remotely on gridengine clusters \\
		\cranpkg{SCORPIUS} & aut & CRAN & 4520 & Inferring developmental chronologies from single-cell RNA sequencing data \\ \hline\hline

@@

\section{Sources of funding}
Robrecht Cannoodt was supported by the Fonds Wetenschappelijk Onderzoek (11Y6218N).
